Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-26 Draft/description.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

In the comparison, the following codes are used:
\begin{itemize}
 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator
and matrix elements taken from several sources: Born matrix elements are
adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic
processes, real matrix elements are written by Marina Billoni, and virtual
matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library
\cite{Denner:2014gla,Denner:2016kdg}.

@@

  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states at $\Pp \Pp,\, \Pp\bar{\Pp}$
  and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alpha^4\alphas^2$ including interferences between the two sets of diagrams.
It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity
formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}. The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive
strategy~\cite{Lepage:1977sw}. {\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.

@@

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO}~\cite{MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

@@

%
%

>>>>

In the comparison, the following codes are used:

\begin{itemize}

 \item The program {\sc Bonsay} consists of a general-purpose Monte Carlo integrator and matrix elements taken from several sources.
 Born matrix elements are adapted from the program {\sc Lusifer} \cite{Dittmaier:2002ap} for the partonic processes, real matrix elements are written by Marina Billoni, and virtual matrix elements by Stefan Dittmaier.
One loop integrals are evaluated using the {\sc Collier} library~\cite{Denner:2014gla,Denner:2016kdg}.

@@

  \item {\sc Phantom}~\cite{Ballestrero:2007xq} is a dedicated tree-level Monte Carlo for six parton final states 
  at $\Pp \Pp,\, \Pp\bar{\Pp}$ and $\Pe^+\Pe^-$ colliders at orders $\alpha^6$ and $\alphas^2\alpha^4$ including interferences between the two sets of diagrams.
It employs complete tree-level matrix elements in the complex-mass scheme~\cite{Denner:2006ic} computed via the modular helicity formalism~\cite{Ballestrero:1999md,Ballestrero:1994jn}.
The integration uses a multichannel approach~\cite{Berends:1984gf} and an adaptive strategy~\cite{Lepage:1977sw}.
{\sc Phantom} generates unweighted events at parton level for both the SM and a few instances of BSM theories.

@@

\item The program {\sc MoCaNLO+Recola} is made of a flexible Monte Carlo program dubbed {\sc MoCaNLO} and of the general matrix element generator {\sc Recola}~\cite{Actis:2012qn,Actis:2016mpe}.
The fast integration is ensured by using similar phase-space mappings to those of Refs.~\cite{Berends:1994pv,Denner:1999gp,Dittmaier:2002ap}.
The IR divergences appearing in the real corrections are handles with the help of the Cantani--Seymour dipole formalism \cite{Catani:1996vz,Dittmaier:1999mb}.
To numerically evaluate the one-loop scalar and tensor integrals, {\sc Recola} relies on the {\sc Collier} library \cite{Denner:2014gla,Denner:2016kdg}.
These tools have been successfully used for the computation of NLO corrections for high-multiplicity processes and in particlar VBS~\cite{Biedermann:2016yds,Biedermann:2017bss}.

@@

### 2018-01-26 Draft/input.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

We simulate VBS production at the LHC, with a center-of-mass energy $\sqrt s = 13 \TeV$. We assume five massless flavours in the proton, and employ the NNPDF~3.0 parton
density~\cite{Ball:2014uwa}
with NLO QCD evolution (the {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} for this set is 260000) and strong coupling constant $\alphas\left( \MZ \right) = 0.118$. Since
the employed PDF set has no photonic density, photon-induced processes are not considered. Initial-state collinear singularities are factorised with the  ${\overline{\rm MS}}$
scheme, consistently with what is done in NNPDF.\\
We use the following values for the mass and width of the massive particles:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
and renormalise the EW coupling in the $G_\mu$ scheme \cite{Denner:2000bj} where
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
The derived value of the EW coupling $\alpha$, corresponding to our choice of input parameters, is
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}. \\
\end{equation}
We employ the complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} to treat unstable intermediate particles in a gauge-invariant manner {\bf CHECK THAT ALL CODES USE THE CMS}.\\

The renormalisation and factorisation scales are set dynamically as
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}},
\end{equation}

Cross sections and distribution are computed within the following VBS cuts inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}:
\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

>>>>

The VBS production mechanism is simulated at the LHC with a center-of-mass energy $\sqrt s = 13 \TeV$. 
The five flavour scheme is used and the NNPDF~3.0 parton density~\cite{Ball:2014uwa} with NLO QCD evolution is employed and strong coupling constant $\alphas\left( \MZ \right) = 0.118$.\footnote{The corresponding {\tt lhaid} in LHAPDF6~\cite{Buckley:2014ana} is 260000.} 
Since the employed PDF set has no photonic density, photon-induced processes are not considered.
Initial-state collinear singularities are factorised with the ${\overline{\rm MS}}$ scheme, consistently with what is done in NNPDF.

For the mass and width of the massive particles, the following values are used:
%
\begin{alignat}{2}
                  \Mt   &=  173.21\GeV,       & \quad \quad \quad \Gt &= 0 \GeV,  \nonumber \\
                \MZOS &=  91.1876\GeV,      & \quad \quad \quad \GZOS &= 2.4952\GeV,  \nonumber \\
                \MWOS &=  80.385\GeV,       & \GWOS &= 2.085\GeV,  \nonumber \\
                M_{\rm H} &=  125.0\GeV,       &  \GH   &=  4.07 \times 10^{-3}\GeV,
\end{alignat}
%
and the EW coupling is renormalised in the $G_\mu$ scheme \cite{Denner:2000bj} where
%
\begin{equation}
    G_{\mu}    = 1.16637\times 10^{-5}\GeV^{-2}.
\end{equation}
%
The numerical value of $\alpha$, corresponding to the choice of input parameters, is
%
\begin{equation}
 \alpha = 7.555310522369 \times 10^{-3}.
\end{equation}
%
The complex-mass scheme~\cite{Denner:1999gp,Denner:2005fg} is used throughout to treat unstable intermediate particles in a gauge-invariant manner.

The renormalisation and factorisation scales are set dynamically to
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}.
\end{equation}
%
This choice of scale has been shown to provide stable NLO predictions \cite{Denner:2012dz}.

The cross sections and distribution are computed within the following event selecton.
These are inspired from experimental measurements \cite{Aad:2014zda,Aaboud:2016ffv,Khachatryan:2014sta,CMS:2017adb}.

\begin{itemize}
    \item The two same-sign charged leptons are required to have
        \begin{align}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos in the event,
        is required to be
        \begin{align}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. Jets are required
        to have
        \begin{align}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        On the two jets with largest transverse-momentum the following invariant-mass and rapidity-separation cuts are imposed
        \begin{align}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5.
        \end{align}
%         Finally, all jest in the event are required to be separated from charged leptons:
%         \begin{align}
%          \qquad\Delta R_{\Pj\Pl} > 0.3 .
%         \end{align}
    \item When EW corrections are computed, real photons and charged fermion are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks mentioned above must be understood as {\it dressed fermions}. Photons
        which are not combined at this step are clustered with QCD partons to form jets as it is described previously.
\end{itemize}

### 2018-01-26 Draft/introduction.tex
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge- and unitarity cancellations that strongly depend on the actual form of the Higgs-sector.
A detailed study of this class of processes will therefore further constrain the Higgs-couplings and hint at or exclude non-Standard Model Higgs bosons.

The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \TeV data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \TeV data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because the double-charge structure of the leptonic final state limits the number of partonic processes and total number of Feynman diagrams for each process.
It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg $\PW^+\PW^-$ scattering, which has the largest cross section.
Therefore, it is an ideal candidate for a detailed study of various theoretical predictions.

In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
These computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
Preliminary results have already been made public in Ref.~[proceedings Split].

The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to identify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on; in this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
To our knowledge, such a detailed study was still missing.

@@

Obviously all VBS processes deserve such a study but the present article sets the standard for inferring systematics related to NLO corrections and beyond.

The article is organised as follow:
In Sec.~\ref{sec:definition} the studied process is defined.
Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
This is followed by a presentation of the programs used for the computations.
Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
Section~\ref{sec:matching} deals with the matching to parton shower.
The last section consists in concluding remarks and recommendations for experimental collaborations.

>>>>

Vector-boson scattering (VBS) is a class of processes that allow to probe the nature of Higgs-vector-vector couplings and quartic gauge couplings.
It is usually understood that VBS refers to the scattering of massive vector-bosons ($\PW^\pm,\PZ$), which therefore couple to the Higgs boson and can be longitudinally polarized.
The scattering of longitudinally polarized bosons is of particular interest, because the corresponding matrix elements feature both gauge and unitarity cancellations that strongly depend on the actual form of the Higgs sector.
A detailed study of this class of processes will therefore further constrain the Higgs couplings and hint at or exclude non-Standard Model Higgs bosons.

The process with two positively charged W bosons is the VBS process with the largest signal-to-background ratio at the LHC, for which evidence has been found in $8 \TeV$ data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in $13\TeV$ data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

The $\PW^+\PW^+$ scattering is the simplest VBS process to calculate, because of the double-charge structure of the leptonic final state that limits the number of partonic processes and total number of Feynman diagrams for each process.
It also implies that irreducible backgrounds are comparatively small, which make this VBS process experimentally favourable in comparison to \eg to $\PW^+\PW^-$ scattering, which has the largest cross section.
Therefore, the $\PW^+\PW^+$ scattering is an ideal candidate for a detailed study of various theoretical predictions.

In the last few years, several leading order (LO) and next-to-leading order (NLO) computations became available for both the VBS process~\cite{Jager:2009xx,Jager:2011ms,Denner:2012dz,Rauch:2016pai} and its QCD-induced irreducible background process~\cite{Rauch:2016pai,Melia:2010bm,Melia:2011gk,Campanario:2013gea,Baglio:2014uba}.
These computations all rely on approximations, while recently the complete NLO corrections have been performed~\cite{Biedermann:2017bss}.
It is therefore interesting to infer in details the quality of the various approximations.
Indeed, apart from Ref.~\cite{Biedermann:2017bss} where it is commented on, \MP{more references?} no detailed comparison of the VBS approximations have been carried out.
Preliminary results have already been made public in %Ref.~\cite{Anders:2018gfr}.

The hadronic process is $\Pp\Pp\to\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj+\mathrm{X}$, which includes the $\PW^+\PW^+$ scattering.
This final state possesses three contributions at LO whose coupling orders are $\mathcal{O}{\left(\alpha^{6}\right)}$, $\mathcal{O}{\left(\alpha_{\rm s}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{2}\alpha^{4}\right)}$.
They are commonly referred to as electroweak (EW), interference, and QCD contributions, respectively.%
\footnote{The EW contribution is sometimes referred to as the VBS contribution even it possesses non-VBS contributions.}
Therefore, the present work starts with a LO study of these three contributions as a function of typical VBS cuts.
This allows to quantify the various contributions to the final state $\mu^+\nu_\mu{\rm e}^+\nu_{\rm e}\,\Pj\Pj$.
This is followed by a LO comparison between the various predictions at the level of the cross section and differential distributions.

At NLO, the process possesses four contributions of orders $\mathcal{O}{\left(\alpha^{7}\right)}$, $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$, $\mathcal{O}{\left(\alphas^{2}\alpha^{5}\right)}$, and $\mathcal{O}{\left(\alphas^{3}\alpha^{4}\right)}$.
The largest one are the EW corrections~\cite{Biedermann:2017bss,Biedermann:2016yds} of order $\mathcal{O}{\left(\alpha^{7}\right)}$.
The contribution to the order $\mathcal{O}{\left(\alphas\alpha^{6}\right)}$ is the second largest NLO contribution and is often referred to as the QCD corrections to the VBS process.
In the following, this order is the one where our comparisons are focused on.
In this article we will refer to it as simply \emph{NLO}.
As for the LO study, the various predictions are compared at the level of the cross section and differential distributions.
In particular, this allows to infer the accuracy of the so-called VBS approximation, which we will define in more detail later.
To our knowledge, such a detailed study was still missing.

@@

Obviously all VBS processes deserve such a detailed study but the present article sets standards for inferring systematics related to NLO corrections and beyond.

The article is organised as follow:
in Sec.~\ref{sec:definition} the studied process is defined.
Various approximation at LO and NLO are described in Sec.~\ref{sec:details}.
This is followed by a presentation of the programs used for the computations.
Sections~\ref{sec:LO} and \ref{sec:NLO} are devoted to a LO and NLO study, respectively.
Section~\ref{sec:matching} deals with the matching to parton shower.
The last section consists in concluding remarks and recommendations for experimental collaborations.

### 2018-01-26 Draft/shower.tex
fix a bunch of typos
Some extra corrections added. Note that I struggled to get the draft working. It seems that it was related to some bibliography issues. I tried to clean up the bib file a bit (is there a maximum number of item in .bib file?). I also had to clean all the non .tex and .bib files generated when compiling. It seems to work now on my computer but you might also have issues.

We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
{\sc MG5\_aMC},
which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3) 
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8} 
{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
matching, in both cases together with {\sc Herwig7}~\cite{}. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\

Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all) 
must be emplouyed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\

>>>>

We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
{\sc MG5\_aMC},
which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3)
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\

Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all)
must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\
